# Comparing catch

```{r required, echo=FALSE,message=FALSE}
library(fields)
library(lattice)
library(colorspace)
require(RCurl)
require(ggplot2)
require(ggthemes)
```


```{r loadData, echo=FALSE, message=FALSE}
#sim=read.csv("~/Desktop/noMPAnotThresh_add_2013-12-09.csv")
# for emma's local copy
  #sim=read.csv("/Users/efuller/Documents/Projects/Moving_fish/MovingFish/Simluations/Aspatial_fast/Data/nothresh/noMPAnotThresh_add_2013-12-09.csv")

# for synced online github data
  x = getURL("https://raw.github.com/emfuller/MovingFish/master/Simluations/Aspatial_fast/Data/nothresh/noMPAnotThresh_add_2013-12-09.csv?token=3235371__eyJzY29wZSI6IlJhd0Jsb2I6ZW1mdWxsZXIvTW92aW5nRmlzaC9tYXN0ZXIvU2ltbHVhdGlvbnMvQXNwYXRpYWxfZmFzdC9EYXRhL25vdGhyZXNoL25vTVBBbm90VGhyZXNoX2FkZF8yMDEzLTEyLTA5LmNzdiIsImV4cGlyZXMiOjEzOTEyNjg5OTB9--e041d4ef68764b1fc49140c128bda685c6f740f3")
  sim = read.csv(textConnection(x))

  fish = getURL("https://raw.github.com/emfuller/MovingFish/master/Simluations/Aspatial_fast/Data/nothresh/fishMPAnotThresh_add_2013-12-09.csv?token=3235371__eyJzY29wZSI6IlJhd0Jsb2I6ZW1mdWxsZXIvTW92aW5nRmlzaC9tYXN0ZXIvU2ltbHVhdGlvbnMvQXNwYXRpYWxfZmFzdC9EYXRhL25vdGhyZXNoL2Zpc2hNUEFub3RUaHJlc2hfYWRkXzIwMTMtMTItMDkuY3N2IiwiZXhwaXJlcyI6MTM5MTI2OTAzM30%3D--f35f2593a7e901c900188fadca920fdd68a57e35")
  fishmpa = read.csv(textConnection(fish))

  cons = getURL("https://raw.github.com/emfuller/MovingFish/master/Simluations/Aspatial_fast/Data/nothresh/consMPAnotThresh_add_2014-01-23.csv?token=3235371__eyJzY29wZSI6IlJhd0Jsb2I6ZW1mdWxsZXIvTW92aW5nRmlzaC9tYXN0ZXIvU2ltbHVhdGlvbnMvQXNwYXRpYWxfZmFzdC9EYXRhL25vdGhyZXNoL2NvbnNNUEFub3RUaHJlc2hfYWRkXzIwMTQtMDEtMjMuY3N2IiwiZXhwaXJlcyI6MTM5MTI2OTA3Mn0%3D--ffb8451d33daaeab48f8b3be3357cacbda0aadbb")
  consmpa = read.csv(textConnection(cons))

# combine all data into one dataframe

sim$management = rep("noManagement",nrow(sim))
consmpa$management = rep("consMPA", nrow(consmpa))
fishmpa$management = rep("fishMPA", nrow(fishmpa))

allData <- rbind(sim,consmpa,fishmpa)
```

Map equilibrium harvest as function of speed of climate velocity and harvest rate.

```{r Compare_Management,echo = FALSE, fig.width=10, fig.height=10}
contourplot(Equil.harvest ~ speed * harvest | factor(management), data = allData, region=TRUE, layout = c(1,3), drape=TRUE)

```

Looks like conservation MPAs do the best at the highest amount of harvest rates. Wonder if there's a difference in variance among these different MPAs. Subsetting the data to just look at harvest rate = 0.04 I find that the conservation MPA seems to have the most variance around average catch. 

```{r variance, echo = FALSE, fig.width=10, fig.height=5}
subData <- subset(allData,harvest == 0.04 )
pd <- position_dodge(.1)
ggplot(subData, aes(x = speed, y = Equil.harvest))+ facet_wrap(~management) + geom_line() + geom_ribbon(aes(ymin = Equil.harvest - Equil.harvest.se, ymax = Equil.harvest + Equil.harvest.se), alpha = 0.35) + theme_bw()
```

Trying the same plot but a higher rate of catch: $$h = 0.10$$ I get,

```{r variance_high, echo = FALSE, fig.width=10, fig.height=5}
subData <- subset(allData,harvest == 0.10 )
pd <- position_dodge(.1)
ggplot(subData, aes(x = speed, y = Equil.harvest))+ facet_wrap(~management) + geom_line() + geom_ribbon(aes(ymin = Equil.harvest - Equil.harvest.se, ymax = Equil.harvest + Equil.harvest.se), alpha = 0.35) + theme_bw()
```

Looking at holding speed constant and examining catch as a function of harvest

```{r harvestVar, echo = FALSE, fig.width=10, fig.height=5}
subData <- subset(allData,speed==0.1)
ggplot(subData, aes(x = harvest, y = Equil.harvest)) + facet_wrap(~management) + geom_line() + geom_ribbon(aes(ymin = Equil.harvest - Equil.harvest.se, ymax = Equil.harvest + Equil.harvest.se), alpha = 0.35) + theme_bw()

subData <- subset(allData,speed==0.2)
ggplot(subData, aes(x = harvest, y = Equil.harvest)) + facet_wrap(~management) + geom_line() + geom_ribbon(aes(ymin = Equil.harvest - Equil.harvest.se, ymax = Equil.harvest + Equil.harvest.se), alpha = 0.35) + theme_bw()

subData <- subset(allData,speed==0.3)
ggplot(subData, aes(x = harvest, y = Equil.harvest)) + facet_wrap(~management) + geom_line() + geom_ribbon(aes(ymin = Equil.harvest - Equil.harvest.se, ymax = Equil.harvest + Equil.harvest.se), alpha = 0.35) + theme_bw()
```
