# Effect of MPAs

```{r required, echo=FALSE,message=FALSE}
library(fields)
library(lattice)
library(colorspace)
require(RCurl)
require(ggplot2)
require(ggthemes)
require(plyr)
require(reshape2)
require(RColorBrewer)
```
Have noticed that there's a section of parameter space in which the `Equil.pop` varies in the `consMPA` simulations. Why is that?

```{r loadData, echo=FALSE, message=FALSE}
# for synced online github data
x = getURL("https://raw.github.com/emfuller/MovingFish/master/Simluations/Aspatial_fast/Data/MPAnull_2014-03-02.csv?token=3235371__eyJzY29wZSI6IlJhd0Jsb2I6ZW1mdWxsZXIvTW92aW5nRmlzaC9tYXN0ZXIvU2ltbHVhdGlvbnMvQXNwYXRpYWxfZmFzdC9EYXRhL01QQW51bGxfMjAxNC0wMy0wMi5jc3YiLCJleHBpcmVzIjoxMzk0NDc3MzYwfQ%3D%3D--5fa73caaafffae7c95d930f61def04ee9b96930a")
sim = read.csv(textConnection(x))

fish = getURL("https://raw.github.com/emfuller/MovingFish/master/Simluations/Aspatial_fast/Data/MPAfish_2014-03-02.csv?token=3235371__eyJzY29wZSI6IlJhd0Jsb2I6ZW1mdWxsZXIvTW92aW5nRmlzaC9tYXN0ZXIvU2ltbHVhdGlvbnMvQXNwYXRpYWxfZmFzdC9EYXRhL01QQWZpc2hfMjAxNC0wMy0wMi5jc3YiLCJleHBpcmVzIjoxMzk0NDc3MzQ2fQ%3D%3D--9b6ceb0092173222543c95381dfbb0f42f0c884f")
fishmpa = read.csv(textConnection(fish))

cons = getURL("https://raw.github.com/emfuller/MovingFish/master/Simluations/Aspatial_fast/Data/MPAcons_2014-03-01.csv?token=3235371__eyJzY29wZSI6IlJhd0Jsb2I6ZW1mdWxsZXIvTW92aW5nRmlzaC9tYXN0ZXIvU2ltbHVhdGlvbnMvQXNwYXRpYWxfZmFzdC9EYXRhL01QQWNvbnNfMjAxNC0wMy0wMS5jc3YiLCJleHBpcmVzIjoxMzk0NDc3MzIwfQ%3D%3D--5f4f584256a4175eebe2ef5465e83c92ebe65cc0")
consmpa = read.csv(textConnection(cons))

thresh = getURL("https://raw.github.com/emfuller/MovingFish/master/Simluations/Aspatial_fast/Data/Thresh_2014-03-02.csv?token=3235371__eyJzY29wZSI6IlJhd0Jsb2I6ZW1mdWxsZXIvTW92aW5nRmlzaC9tYXN0ZXIvU2ltbHVhdGlvbnMvQXNwYXRpYWxfZmFzdC9EYXRhL1RocmVzaF8yMDE0LTAzLTAyLmNzdiIsImV4cGlyZXMiOjEzOTQ0ODIyMTV9--13d78257cda683d18eb8ecc71dcf0f4e6101b41d")
threshz = read.csv(textConnection(thresh))

# combine all data into one dataframe
sim$management = rep("No MPAs",nrow(sim))
consmpa$management = rep("Few Large MPAs", nrow(consmpa))
fishmpa$management = rep("Many Small MPAs", nrow(fishmpa))
threshz$management = rep("Thresholds", nrow(threshz))
allData <- rbind(sim,consmpa,fishmpa)
```
Map equilibrium harvest as function of speed of climate velocity and harvest rate.

```{r Compare_Management,echo = FALSE, fig.width=10, fig.height=10}
sb <- trellis.par.get("strip.background") 
sb[["col"]][1] <- "lightgray"
trellis.par.set("strip.background", sb) 

ltheme <- canonical.theme(color = FALSE) ## in-built B&W theme 
ltheme$strip.background$col <- "transparent" ## change strip bg 
lattice.options(default.theme = ltheme) ## set as default 

lw <- list(left.padding = list(x = 0, units = "inches")) 
lw$right.padding <- list(x = -0.1, units = "inches") 
lh <- list(bottom.padding = list(x = 0, units = "inches")) 
lh$top.padding <- list(x = -0.2, units = "inches")

lattice.options(layout.widths = lw, layout.heights = lh) 

pdf(file="foo.pdf",width=3,height=6)
contourplot(Equil.pop ~ speed * harvest | factor(management), data = allData, region=TRUE, layout = c(1,3), drape=TRUE,col.regions=rev(colorRampPalette(brewer.pal(9,"Greys"))(100)),colorkey=FALSE,labels=list(cex=.75,col="white"))
dev.off()


contourplot(Equil.pop ~ speed * -thresh | factor(management), data = threshz, region=TRUE, drape=TRUE,col.regions=rev(colorRampPalette(brewer.pal(9,"Greys"))(100)),colorkey=FALSE,labels=list(cex=.75,col="white"),scales=list( y=list(at=seq(-8,0,2),labels=round(rev(unique(threshz$thresh)/max(threshz$thresh)),3))),ylab=list(label="proportion of unharvested population below threshold"))

# replicating our figure plots

# build dataframe

```

Looks like conservation MPAs do the best, but there are some weird fluctuations at higher harvest rates, why is that? Can take slices to look more closely

```{r variance, echo = FALSE, fig.width=10, fig.height=5}
subData <- subset(allData,harvest == 0.04 )
pd <- position_dodge(.1)
ggplot(subData, aes(x = speed, y = Equil.pop))+ facet_wrap(~management) + geom_line() + geom_ribbon(aes(ymin = Equil.pop - Equil.pop.se, ymax = Equil.pop + Equil.pop.se), alpha = 0.35) + theme_bw()
```

Trying the same plot but a higher rate of catch: $h = 0.10$ I get,

```{r variance_high, echo = FALSE, fig.width=10, fig.height=5}
subData <- subset(allData,harvest == 0.10 )
pd <- position_dodge(.1)
ggplot(subData, aes(x = speed, y = Equil.pop))+ facet_wrap(~management) + geom_line() + geom_ribbon(aes(ymin = Equil.pop - Equil.pop.se, ymax = Equil.pop + Equil.pop.se), alpha = 0.35) + theme_bw()
```

The relevant section of parameter space is shown below

```{r sub, echo=FALSE,fig.width=15, fig.height=5}
subData <- subset(allData,harvest > 0.05 & harvest < 0.13 & management == "consMPA" & speed < 0.3)
contourplot(Equil.pop ~ speed * harvest, data = subData, region = TRUE, drape = TRUE)
```

The next step is to run a few of these simulations and save entire outputs (biomass over space/time). Will do $h = 0.10, s = 0.02-0.07$ 

```{r sim, echo=FALSE,fig.keep='none',message=FALSE,results='hide'}
setwd("/Users/efuller/Documents/Projects/Moving_fish/MovingFish/Simluations/Aspatial_fast")
source("Parameters.R")
source("Functions.R")
require(zoo)
require(plyr)
require(lattice)
require(dplyr)
require(reshape)
steps = 300   # setting number of steps over which to take equilibrium 
source("Figures/variable_steps.R")
sims300 = sims
df300 = df
series300 = series
notify("Simulation is finished!")
```
After re-running the model, can see that it replicates the pattern of fluctuating total biomas
```{r final-plot,echo=FALSE,message=FALSE,results='hide'}
finals300 <- llply(series300,mean)
sd300 <- llply(series300,sd)
sd300 <- melt(sd300)
df_finals300 <- melt(finals300)
df_finals300$sd = sd300$value
names(df_finals300) <- c("totalPop","Speed","sd")
df_finals300$Speed = speeds
xyplot(totalPop ~ Speed, data=df_finals300,type='l',lwd=2,xlab="Speed", main = "300 steps")
ggplot(df_finals300,aes(x = Speed, y = totalPop)) + geom_errorbar(aes(ymin=totalPop - sd, ymax = totalPop + sd)) + geom_line() + geom_point()

```
And when you look at the time-series population trends, it's as we expected. All the populations have the same pattern, that they oscillate up and down depending on whether or not they're in a reserve, but the slowest speeds go through the biggest oscillations which means that the average population is much lower. However I wonder if just extending the number of time steps over which I run the average would reduce this effect. 
```{r time-series,echo=FALSE,message=FALSE,results='hide'}
  xyplot(sums ~ time | speed, data = df300, type='l',xlab="time",ylab="Population biomass",lwd=2, main = "300 steps")
```
After re-running the simulation (this time with 600 time steps for equilibrium)
```{r second-sim,echo=FALSE,fig.keep='none',message=FALSE,results='hide'}
# pre-allocating list to save simulations

steps = 600   # setting number of steps over which to take equilibrium 
source("Figures/variable_steps.R")
sims600 = sims
df600 = df
series600 = series
notify("Simulation is finished!")
```

```{r plots,echo=FALSE,message=FALSE,results='hide'}
  xyplot(sums ~ time | factor(speed), data = df600, type='l',xlab="time",ylab="Population biomass",lwd=2, main = "600 steps")

finals600 <- llply(series600,mean)
df_finals600 <- melt(finals600)
names(df_finals600) <- c("totalPop","Speed")
df_finals600$Speed = speeds
xyplot(totalPop ~ Speed, data=df_finals600,type='l',lwd=2,xlab="Speed")
```

This seems to matter a little bit

```{r compare,echo=FALSE,message=FALSE,results='hide'}
plot(speeds,df_finals300$totalPop,pch=19,type="o",main="Mean")
lines(speeds,df_finals600$totalPop,col="red",type="o",pch=19)
```

This is weird, shouldn't be like this, not sure why it is. Needs more work. Next step is to try 900 steps to see if the equilibrium varies

```{r thirdSim, echo=FALSE,fig.keep='none'}
steps = 900   # setting number of steps over which to take equilibrium 
source("Figures/variable_steps.R")
sims900 = sims
df900 = df
series900 = series

xyplot(sums ~ time | factor(speed), data = df900, type='l',xlab="time",ylab="Population biomass",lwd=2, main="900 steps")

finals900 <- llply(series900,mean)
df_finals900 <- melt(finals900)
names(df_finals900) <- c("totalPop","Speed")
df_finals900$Speed = speeds
xyplot(totalPop ~ Speed, data=df_finals900,type='l',lwd=2,xlab="Speed")

plot(speeds,df_finals300$totalPop,pch=19,type="o",main="Mean")
lines(speeds,df_finals600$totalPop,col="red",type="o",pch=19)
lines(speeds,df_finals900$totalPop,col="blue", type="o",pch=19)

```


```{r fourthSim, echo=FALSE,fig.keep='none'}
steps = 1200   # setting number of steps over which to take equilibrium 
source("Figures/variable_steps.R")
sims1200 = sims
df1200 = df
series1200 = series

xyplot(sums ~ time | factor(speed), data = df1200, type='l',xlab="time",ylab="Population biomass",lwd=2, main="1200 steps")

finals1200 <- llply(series1200,mean)
df_finals1200 <- melt(finals1200)
names(df_finals1200) <- c("totalPop","Speed")
df_finals1200$Speed = speeds
xyplot(totalPop ~ Speed, data=df_finals1200,type='l',lwd=2,xlab="Speed")

plot(speeds,df_finals300$totalPop,pch=19,type="o",main="Mean")
lines(speeds,df_finals600$totalPop,col="red",type="o",pch=19)
lines(speeds,df_finals900$totalPop,col="blue", type="o",pch=19)
lines(speeds,df_finals1200$totalPop,col="green", type="o",pch=19)

notify("simluation is done!")
```

```{r fifthSim, echo=FALSE,fig.keep='none'}
steps = 1500   # setting number of steps over which to take equilibrium 
source("Figures/variable_steps.R")
sims1500 = sims
df1500 = df
series1500 = series

xyplot(sums ~ time | factor(speed), data = df1500, type='l',xlab="time",ylab="Population biomass",lwd=2, main="1500 steps")

finals1500 <- llply(series1500,mean)
df_finals1500 <- melt(finals1500)
names(df_finals1500) <- c("totalPop","Speed")
df_finals1500$Speed = speeds
xyplot(totalPop ~ Speed, data=df_finals1500,type='l',lwd=2,xlab="Speed")

plot(speeds,df_finals300$totalPop,pch=19,type="o",main="Mean")
lines(speeds,df_finals600$totalPop,col="red",type="o",pch=19)
lines(speeds,df_finals900$totalPop,col="blue", type="o",pch=19)
lines(speeds,df_finals1200$totalPop,col="green", type="o",pch=19)
lines(speeds,df_finals1500$totalPop,col="purple", type="o",pch=19)

notify("simluation is done!")
```

```{r sixthSim, echo=FALSE,fig.keep='none'}
steps = 1800   # setting number of steps over which to take equilibrium 
source("Figures/variable_steps.R")
sims1800 = sims
df1800 = df
series1800 = series

xyplot(sums ~ time | factor(speed), data = df1800, type='l',xlab="time",ylab="Population biomass",lwd=2, main="1800 steps")

finals1800 <- llply(series1800,mean)
df_finals1800 <- melt(finals1800)
names(df_finals1800) <- c("totalPop","Speed")
df_finals1800$Speed = speeds
xyplot(totalPop ~ Speed, data=df_finals1800,type='l',lwd=2,xlab="Speed")

require(RColorBrewer)
colz <- colorRampPalette(brewer.pal(6,"Dark2"))(6)

plot(speeds,df_finals300$totalPop,pch=19,type="o",main="Mean", col=colz[1], lwd=3, bty="n")
lines(speeds,df_finals600$totalPop,col=colz[2],type="o",pch=19,lwd=3)
lines(speeds,df_finals900$totalPop,col=colz[3], type="o",pch=19,lwd=3)
lines(speeds,df_finals1200$totalPop,col=colz[4], type="o",pch=19,lwd=3)
lines(speeds,df_finals1500$totalPop,col=colz[5], type="o",pch=19,lwd=3)
lines(speeds,df_finals1800$totalPop,col=colz[6], type="o",pch=19,lwd=3)

legend("topright",legend=seq(300,1800,300), lwd=3, pch=19,col=colz, title="Steps", bty="n")

notify("simluation is done!")
```

```{r sixthSim, echo=FALSE,fig.keep='none'}
steps = 2100   # setting number of steps over which to take equilibrium 
source("Figures/variable_steps.R")
sims2100 = sims
df2100 = df
series2100 = series

xyplot(sums ~ time | factor(speed), data = df2100, type='l',xlab="time",ylab="Population biomass",lwd=2, main="2100 steps")

finals2100 <- llply(series2100,mean)
df_finals2100 <- melt(finals2100)
names(df_finals2100) <- c("totalPop","Speed")
df_finals2100$Speed = speeds
xyplot(totalPop ~ Speed, data=df_finals2100,type='l',lwd=2,xlab="Speed")

require(RColorBrewer)
colz <- colorRampPalette(brewer.pal(6,"Dark2"))(7)

plot(speeds,df_finals300$totalPop,pch=19,type="o",main="Mean", col=colz[1], lwd=3, bty="n")
lines(speeds,df_finals600$totalPop,col=colz[2],type="o",pch=19,lwd=3)
lines(speeds,df_finals900$totalPop,col=colz[3], type="o",pch=19,lwd=3)
lines(speeds,df_finals1200$totalPop,col=colz[4], type="o",pch=19,lwd=3)
lines(speeds,df_finals1500$totalPop,col=colz[5], type="o",pch=19,lwd=3)
lines(speeds,df_finals1800$totalPop,col=colz[6], type="o",pch=19,lwd=3)
lines(speeds,df_finals2100$totalPop,col=colz[7], type="o",pch=19,lwd=3)

legend("topright",legend=seq(300,2100,300), lwd=3, pch=19,col=colz, title="Steps", bty="n")

notify("simluation is done!")
```

Idea, can I sub-sample the 2100 step run and take the mean of an increasingly limited window? This would mean using `df2100` as the data frame and taking the mean of all 2100 steps, and then 2099 steps, ... etc. down to 300 and seeing how the mean changes. 

```{r}
int <- seq(300,2100)
names(series2100) = speeds
foo <- melt(series2100)
names(foo) <- c("biomass","speed")
means = vector("list",length(int))
names(means) = int
for(i in 1:length(int)){
  means[[i]] = ddply(foo,.(speed),function(df) avg = mean(df$biomass[1:int[i]]))
  }

bar = melt(means)
bar$variable = NULL
names(bar) = c("speed", "mean", "interval")
bar$interval = as.numeric(bar$interval)
ggplot(bar, aes(x = interval , y = mean))  + geom_line() + facet_wrap( ~ speed)
```

New idea, find the maxima and minima and take the mean of those two numbers. See if that erases the variability in means. 

```{r}
int <- seq(300,2100)
names(series2100) = speeds
foo <- melt(series2100)
names(foo) <- c("biomass","speed")
means_dif = vector("list",length(int))
names(means) = int
for(i in 1:length(int)){
  means_dif[[i]] = ddply(foo,.(speed),function(df) avg=mean(max(df$biomass[1:int[i]]),min(df$biomass[1:int[i]])))
  }

bar = melt(means_dif)
bar$variable = NULL
names(bar) = c("speed", "mean", "interval")
bar$interval = as.numeric(bar$interval)
ggplot(bar, aes(x = interval , y = mean))  + geom_line() + facet_wrap( ~ speed)

ggplot(bar, aes(x = speed, y = mean, group = interval)) + geom_line(aes(colour=interval))
```

And volia! It erases that variability. Looks like I can keep the 300 time steps and take the max and minimum and take the average. So should re-do that for the existing simulation data I have and plot a contour map

UPDATE, the problem persists. Malin's idea is to take a time step where the MPA and the range line up at the 'northern' edge. Because the world is only a patch length long, need to figure out when the MPA is at the northern-most edge.